---
title: "Analysis code for Usability Experiment data"
output: html_document
date: "2024-04-26"
author: Susanna Ankama
---

```{r}

wd = getwd()
setwd(wd)

library(readxl)

data <- read_excel("raw_data_final.xlsx")

data$Culture <- as.factor(data$Culture)  
data$DisplayType <- as.factor(data$DisplayType)  
data$QueryType <- as.factor(data$QueryType)
data$GeoportalFrequency <- as.factor(data$GeoportalFrequency)
data$Age <- as.factor(data$Age)

```

## Data Preparation

```{r}

namibian <- data[data$Culture=="namibian", ]
german <- data[data$Culture=="german", ]

lb  <- data[data$DisplayType=="LB", ]
lbm <- data[data$DisplayType=="LBM", ]

st <-  data[data$QueryType=="ST", ]
stt <- data[data$QueryType=="STT", ]

# load libraries, set the number of resamples to 5000
library(bootES)
library(ggplot2)
library(dplyr) 

N_resamples = 5000

```

## Search Effectiveness - DCG\@3
```{r}
# SpatialAnalysis could have possibly affected the ratings
DCG3Model <- lm (DCG3 ~ DisplayType + Culture + QueryType + BasicComputerSkills + SpatialAnalysis + Webgis 
                 + WebmapUse + Programming + GeodataSearching + MapMaking + GeoportalFrequency, data = data)
summary(DCG3Model)

ggplot(data, aes(y = DCG3, x= DisplayType, fill=DisplayType)) +
  geom_boxplot() +  scale_fill_manual(values = c("#94d0f2", "#edd882"))
bootES(data, R=N_resamples, data.col="DCG3", group.col="DisplayType", contrast= c("LB", "LBM"))

# boxplot(ComplexityRatings ~ Culture, data=data)
ggplot(data, aes(y = DCG3, x= QueryType, fill=QueryType)) +
  geom_boxplot() +  scale_fill_manual(values = c("#94d0f2", "#edd882"))
bootES(data, R=N_resamples, data.col="DCG3", group.col="QueryType", contrast= c("ST", "STT"))

# boxplot(ComplexityRatings ~ Culture, data=data)
ggplot(data, aes(y = DCG3, x= Culture, fill=Culture)) +
  geom_boxplot() +  scale_fill_manual(values = c("#94d0f2", "#edd882"))
bootES(data, R=N_resamples, data.col="DCG3", group.col="Culture", contrast= c("namibian", "german"))

# Interaction effects
boxplot(DCG3 ~ DisplayType * Culture, data = data)
boxplot(DCG3 ~ QueryType * Culture, data = data)
boxplot(DCG3 ~ QueryType * DisplayType, data = data)


dcg3DC <- lm (DCG3 ~ DisplayType * Culture, data = data)
dcg3QC <- lm (DCG3 ~ QueryType * Culture, data = data)
dcg3QD <- lm (DCG3 ~ QueryType * DisplayType, data = data)
summary(dcg3DC)
summary(dcg3QC)
summary(dcg3QD)

# testing interaction more systematically
#complexityQC_reduced <- lm (DCG3 ~ QueryType + Culture, data = data)
#anova(complexityQC, complexityQC_reduced)

interaction.plot(x.factor = data$DisplayType, 
                 trace.factor = data$Culture,  
                 response = data$DCG3, fun = mean)

# Obtain the mean, with confidence interval values
# by(data$ComplexityRatings, data$Culture, mean)

bootES(data, R=N_resamples, data.col = "DCG3")

bootES(lb, R=N_resamples, data.col="DCG3")
bootES(lbm, R=N_resamples, data.col="DCG3")

bootES(st, R=N_resamples, data.col="DCG3")
bootES(stt, R=N_resamples, data.col="DCG3")

bootES(namibian, R=N_resamples, data.col="DCG3")
bootES(german, R=N_resamples, data.col="DCG3")



```


## Search Effectiveness - nDCG\@3

```{r}
# no factor affected the results
nDCG3Model <- lm (nDCG3 ~ DisplayType + Culture + QueryType + BasicComputerSkills + SpatialAnalysis + Webgis                  + WebmapUse + Programming + GeodataSearching + MapMaking + GeoportalFrequency, data = data)
summary(nDCG3Model)

ggplot(data, aes(y = nDCG3, x= DisplayType, fill=DisplayType)) +
  geom_boxplot() +  scale_fill_manual(values = c("#94d0f2", "#edd882"))
bootES(data, R=N_resamples, data.col="nDCG3", group.col="DisplayType", contrast= c("LB", "LBM"))

ggplot(data, aes(y = nDCG3, x= QueryType, fill=QueryType)) +
  geom_boxplot() +  scale_fill_manual(values = c("#94d0f2", "#edd882"))
bootES(data, R=N_resamples, data.col="nDCG3", group.col="QueryType", contrast= c("ST", "STT"))

ggplot(data, aes(y = nDCG3, x= Culture, fill=Culture)) +
  geom_boxplot() +  scale_fill_manual(values = c("#94d0f2", "#edd882"))
bootES(data, R=N_resamples, data.col="nDCG3", group.col="Culture", contrast= c("namibian", "german"))

# Interaction effects
boxplot(nDCG3 ~ DisplayType * Culture, data = data)
boxplot(nDCG3 ~ QueryType * Culture, data = data)
boxplot(nDCG3 ~ QueryType * DisplayType, data = data)


ndcg3DC <- lm (nDCG3 ~ DisplayType * Culture, data = data)
ndcg3QC <- lm (nDCG3 ~ QueryType * Culture, data = data)
ndcg3QD <- lm (nDCG3 ~ QueryType * DisplayType, data = data)
summary(ndcg3DC)
summary(ndcg3QC)
summary(ndcg3QD)

# testing interaction more systematically
#complexityQC_reduced <- lm (DCG3 ~ QueryType + Culture, data = data)
#anova(complexityQC, complexityQC_reduced)

interaction.plot(x.factor = data$DisplayType, 
                 trace.factor = data$Culture,  
                 response = data$nDCG3, fun = mean)

# Obtain the mean, with confidence interval values

bootES(data, R=N_resamples, data.col = "nDCG3")

bootES(lb, R=N_resamples, data.col="nDCG3")
bootES(lbm, R=N_resamples, data.col="nDCG3")

bootES(st, R=N_resamples, data.col="nDCG3")
bootES(stt, R=N_resamples, data.col="nDCG3")

bootES(namibian, R=N_resamples, data.col="nDCG3")
bootES(german, R=N_resamples, data.col="nDCG3")


```


## Search Effectiveness - DCG\@5
```{r}
# Culture (and possibley WebMapUse and GeodataSearching skills) have likely affected the results 
DCG5Model <- lm (DCG5 ~ DisplayType + Culture + QueryType + BasicComputerSkills + SpatialAnalysis + Webgis 
                 + WebmapUse + Programming + GeodataSearching + MapMaking + GeoportalFrequency, data = data)
summary(DCG5Model)

ggplot(data, aes(y = DCG5, x= DisplayType, fill=DisplayType)) +
  geom_boxplot() +  scale_fill_manual(values = c("#94d0f2", "#edd882"))
bootES(data, R=N_resamples, data.col="DCG5", group.col="DisplayType", contrast= c("LB", "LBM"))

ggplot(data, aes(y = DCG5, x= QueryType, fill=QueryType)) +
  geom_boxplot() +  scale_fill_manual(values = c("#94d0f2", "#edd882"))
bootES(data, R=N_resamples, data.col="DCG5", group.col="QueryType", contrast= c("ST", "STT"))

# boxplot(ComplexityRatings ~ Culture, data=data)
ggplot(data, aes(y = DCG5, x= Culture, fill=Culture)) +
  geom_boxplot() +  scale_fill_manual(values = c("#94d0f2", "#edd882"))
bootES(data, R=N_resamples, data.col="DCG5", group.col="Culture", contrast= c("namibian", "german"))

# Interaction effects
boxplot(DCG5 ~ DisplayType * Culture, data = data)
boxplot(DCG5 ~ QueryType * Culture, data = data)
boxplot(DCG5 ~ QueryType * DisplayType, data = data)


dcg5DC <- lm (DCG5 ~ DisplayType * Culture, data = data)
dcg5QC <- lm (DCG5 ~ QueryType * Culture, data = data)
dcg5QD <- lm (DCG5 ~ QueryType * DisplayType, data = data)
summary(dcg5DC)
summary(dcg5QC)
summary(dcg5QD)

# testing interaction more systematically
#complexityQC_reduced <- lm (DCG3 ~ QueryType + Culture, data = data)
#anova(complexityQC, complexityQC_reduced)

interaction.plot(x.factor = data$DisplayType, 
                 trace.factor = data$Culture,  
                 response = data$DCG5, fun = mean)

# Obtain the mean, with confidence interval values

bootES(data, R=N_resamples, data.col = "DCG5")

bootES(lb, R=N_resamples, data.col="DCG5")
bootES(lbm, R=N_resamples, data.col="DCG5")

bootES(st, R=N_resamples, data.col="DCG5")
bootES(stt, R=N_resamples, data.col="DCG5")

bootES(namibian, R=N_resamples, data.col="DCG5")
bootES(german, R=N_resamples, data.col="DCG5")


```


## Search Effectiveness - nDCG\@5
```{r}
# no factor affected the ratings
nDCG5Model <- lm (nDCG5 ~ DisplayType + Culture + QueryType + BasicComputerSkills + SpatialAnalysis + Webgis
                 + WebmapUse + Programming + GeodataSearching + MapMaking + GeoportalFrequency, data = data)
summary(nDCG5Model)

ggplot(data, aes(y = nDCG5, x= DisplayType, fill=DisplayType)) +
  geom_boxplot() +  scale_fill_manual(values = c("#94d0f2", "#edd882"))
bootES(data, R=N_resamples, data.col="nDCG5", group.col="DisplayType", contrast= c("LB", "LBM"))

ggplot(data, aes(y = nDCG3, x= QueryType, fill=QueryType)) +
  geom_boxplot() +  scale_fill_manual(values = c("#94d0f2", "#edd882"))
bootES(data, R=N_resamples, data.col="nDCG5", group.col="QueryType", contrast= c("ST", "STT"))

ggplot(data, aes(y = nDCG3, x= Culture, fill=Culture)) +
  geom_boxplot() +  scale_fill_manual(values = c("#94d0f2", "#edd882"))
bootES(data, R=N_resamples, data.col="nDCG5", group.col="Culture", contrast= c("namibian", "german"))

# Interaction effects
boxplot(nDCG5 ~ DisplayType * Culture, data = data)
boxplot(nDCG5 ~ QueryType * Culture, data = data)
boxplot(nDCG5 ~ QueryType * DisplayType, data = data)


ndcg5DC <- lm (nDCG5 ~ DisplayType * Culture, data = data)
ndcg5QC <- lm (nDCG5 ~ QueryType * Culture, data = data)
ndcg5QD <- lm (nDCG5 ~ QueryType * DisplayType, data = data)
summary(ndcg5DC)
summary(ndcg5QC)
summary(ndcg5QD)

# testing interaction more systematically
#complexityQC_reduced <- lm (DCG3 ~ QueryType + Culture, data = data)
#anova(complexityQC, complexityQC_reduced)

interaction.plot(x.factor = data$DisplayType, 
                 trace.factor = data$Culture,  
                 response = data$nDCG5, fun = mean)

# Obtain the mean, with confidence interval values

bootES(data, R=N_resamples, data.col = "nDCG5")

bootES(lb, R=N_resamples, data.col="nDCG5")
bootES(lbm, R=N_resamples, data.col="nDCG5")

bootES(st, R=N_resamples, data.col="nDCG5")
bootES(stt, R=N_resamples, data.col="nDCG5")

bootES(namibian, R=N_resamples, data.col="nDCG5")
bootES(german, R=N_resamples, data.col="nDCG5")


```


## UI Complexity

```{r}

### Culture and MapMaking skills could have possibly affected the ratings
# https://stats.stackexchange.com/questions/160026/why-does-an-insignificant-regressor-become-significant-if-i-add-some-significant
ComplexityModel <- lm (ComplexityRatings ~ DisplayType + Culture + QueryType 
                  + BasicComputerSkills + SpatialAnalysis + Webgis + WebmapUse + Programming 
                  + GeodataSearching + MapMaking + GeoportalFrequency, data = data)
summary(ComplexityModel)


#boxplot(ComplexityRatings ~ DisplayType, data=data)
ggplot(data, aes(y = ComplexityRatings, x= DisplayType, fill=DisplayType)) +
  geom_boxplot() +  scale_fill_manual(values = c("#94d0f2", "#edd882"))
bootES(data, R=N_resamples, data.col="ComplexityRatings", group.col="DisplayType", contrast= c("LB", "LBM"))

# boxplot(ComplexityRatings ~ Culture, data=data)
ggplot(data, aes(y = ComplexityRatings, x= QueryType, fill=QueryType)) +
  geom_boxplot() +  scale_fill_manual(values = c("#94d0f2", "#edd882"))
bootES(data, R=N_resamples, data.col="ComplexityRatings", group.col="QueryType", contrast= c("ST", "STT"))

# boxplot(ComplexityRatings ~ Culture, data=data)
ggplot(data, aes(y = ComplexityRatings, x= Culture, fill=Culture)) +
  geom_boxplot() +  scale_fill_manual(values = c("#94d0f2", "#edd882"))
bootES(data, R=N_resamples, data.col="ComplexityRatings", group.col="Culture", contrast= c("namibian", "german"))

# Interaction effects
boxplot(ComplexityRatings ~ DisplayType * Culture, data = data)
boxplot(ComplexityRatings ~ QueryType * Culture, data = data)
boxplot(ComplexityRatings ~ QueryType * DisplayType, data = data)


complexityDC <- lm (ComplexityRatings ~ DisplayType * Culture, data = data)
complexityQC <- lm (ComplexityRatings ~ QueryType * Culture, data = data)
complexityQD <- lm (ComplexityRatings ~ QueryType * DisplayType, data = data)
summary(complexityDC)
summary(complexityQC)
summary(complexityQD)

# testing interaction more systematically
complexityQC_reduced <- lm (ComplexityRatings ~ QueryType + Culture, data = data)
anova(complexityQC, complexityQC_reduced)

interaction.plot(x.factor = data$DisplayType, 
                 trace.factor = data$Culture,  
                 response = data$ComplexityRatings, fun = mean)

# Obtain the mean, with confidence interval values
bootES(data, R=N_resamples, data.col="ComplexityRatings")

bootES(lb, R=N_resamples, data.col="ComplexityRatings")
bootES(lbm, R=N_resamples, data.col="ComplexityRatings")

bootES(st, R=N_resamples, data.col="ComplexityRatings")
bootES(stt, R=N_resamples, data.col="ComplexityRatings")

bootES(namibian, R=N_resamples, data.col="ComplexityRatings")
bootES(german, R=N_resamples, data.col="ComplexityRatings")


```

## User Experience - SupportiveObstructive

```{r}

# No factor affected the ratings
SupportiveObstructiveModel <- lm (SupportiveObstructive ~ DisplayType + Culture + QueryType 
                  + BasicComputerSkills + SpatialAnalysis + Webgis + WebmapUse + Programming 
                  + GeodataSearching + MapMaking + GeoportalFrequency, data = data)
summary(SupportiveObstructiveModel)


ggplot(data, aes(y = SupportiveObstructive, x= DisplayType, fill=DisplayType)) +
  geom_boxplot() +  scale_fill_manual(values = c("#94d0f2", "#edd882"))
bootES(data, R=N_resamples, data.col="SupportiveObstructive", group.col="DisplayType", contrast= c("LB", "LBM"))

ggplot(data, aes(y = SupportiveObstructive, x= QueryType, fill=QueryType)) +
  geom_boxplot() +  scale_fill_manual(values = c("#94d0f2", "#edd882"))
bootES(data, R=N_resamples, data.col="SupportiveObstructive", group.col="QueryType", contrast= c("ST", "STT"))

ggplot(data, aes(y = SupportiveObstructive, x= Culture, fill=Culture)) +
  geom_boxplot() +  scale_fill_manual(values = c("#94d0f2", "#edd882"))
bootES(data, R=N_resamples, data.col="SupportiveObstructive", group.col="Culture", contrast= c("namibian", "german"))

# Interaction effects
boxplot(SupportiveObstructive ~ DisplayType * Culture, data = data)
boxplot(SupportiveObstructive ~ QueryType * Culture, data = data)
boxplot(SupportiveObstructive ~ QueryType * DisplayType, data = data)


supportiveDC <- lm (SupportiveObstructive ~ DisplayType * Culture, data = data)
supportiveQC <- lm (SupportiveObstructive ~ QueryType * Culture, data = data)
supportiveQD <- lm (SupportiveObstructive ~ QueryType * DisplayType, data = data)
summary(supportiveDC)
summary(supportiveQC)
summary(supportiveQD)

# testing interaction more systematically
supportiveDC_reduced <- lm (SupportiveObstructive ~ DisplayType + Culture, data = data)
anova(supportiveDC, supportiveDC_reduced)

# interaction plot (simple)
interaction.plot(x.factor = data$DisplayType, 
                 trace.factor = data$Culture,  
                 response = data$SupportiveObstructive, fun = mean)

# interaction plot in ggplot2
# https://sebastiansauer.github.io/vis_interaction_effects/
data %>% 
  group_by(DisplayType, Culture) %>% 
  summarise(rating_groups = mean(SupportiveObstructive)) -> ratings2

ratings2 %>% 
  ggplot() +
  aes(x = DisplayType, y = rating_groups, color = Culture) +
  geom_line(aes(group = Culture)) +
  geom_point() + labs(y= "Mean of SupportiveObstructive Ratings")

# Obtain the mean, with confidence interval values

bootES(data, R=N_resamples, data.col="SupportiveObstructive")

bootES(lb, R=N_resamples, data.col="SupportiveObstructive")
bootES(lbm, R=N_resamples, data.col="SupportiveObstructive")

bootES(st, R=N_resamples, data.col="SupportiveObstructive")
bootES(stt, R=N_resamples, data.col="SupportiveObstructive")

bootES(namibian, R=N_resamples, data.col="SupportiveObstructive")
bootES(german, R=N_resamples, data.col="SupportiveObstructive")


```

## User Experience - EasyComplicated

```{r}

# Geodatasearching could have possibly affected the ratings
EasyComplicatedModel <- lm (EasyComplicated ~ DisplayType + Culture + QueryType 
                  + BasicComputerSkills + SpatialAnalysis + Webgis + WebmapUse + Programming 
                  + GeodataSearching + MapMaking + GeoportalFrequency, data = data)
summary(EasyComplicatedModel)

ggplot(data, aes(y = EasyComplicated, x= DisplayType, fill=DisplayType)) +
  geom_boxplot() +  scale_fill_manual(values = c("#94d0f2", "#edd882"))
bootES(data, R=N_resamples, data.col="EasyComplicated", group.col="DisplayType", contrast= c("LB", "LBM"))

ggplot(data, aes(y = EasyComplicated, x= QueryType, fill=QueryType)) +
  geom_boxplot() +  scale_fill_manual(values = c("#94d0f2", "#edd882"))
bootES(data, R=N_resamples, data.col="EasyComplicated", group.col="QueryType", contrast= c("ST", "STT"))

ggplot(data, aes(y = EasyComplicated, x= Culture, fill=Culture)) +
  geom_boxplot() +  scale_fill_manual(values = c("#94d0f2", "#edd882"))
bootES(data, R=N_resamples, data.col="EasyComplicated", group.col="Culture", contrast= c("namibian", "german"))

# Interaction effects
boxplot(EasyComplicated ~ DisplayType * Culture, data = data)
boxplot(EasyComplicated ~ QueryType * Culture, data = data)
boxplot(EasyComplicated ~ QueryType * DisplayType, data = data)


easyDC <- lm (EasyComplicated ~ DisplayType * Culture, data = data)
easyQC <- lm (EasyComplicated ~ QueryType * Culture, data = data)
easyQD <- lm (EasyComplicated ~ QueryType * DisplayType, data = data)
summary(easyDC)
summary(easyQC)
summary(easyQD)

# testing interaction more systematically
easyQC_reduced <- lm (EasyComplicated ~ QueryType + Culture, data = data)
anova(easyQC, easyQC_reduced)

# interaction plot (simple)
interaction.plot(x.factor = data$QueryType, 
                 trace.factor = data$Culture,  
                 response = data$EasyComplicated, fun = mean)

# interaction plot in ggplot2
# https://sebastiansauer.github.io/vis_interaction_effects/
data %>% 
  group_by(QueryType, Culture) %>% 
  summarise(rating_groups = mean(EasyComplicated)) -> ratings2

ratings2 %>% 
  ggplot() +
  aes(x = QueryType, y = rating_groups, color = Culture) +
  geom_line(aes(group = Culture)) +
  geom_point() + labs(y= "Mean of EasyComplicated Ratings")

bootES(data, R=N_resamples, data.col="EasyComplicated")

# Obtain the mean, with confidence interval values
bootES(lb, R=N_resamples, data.col="EasyComplicated")
bootES(lbm, R=N_resamples, data.col="EasyComplicated")

bootES(st, R=N_resamples, data.col="EasyComplicated")
bootES(stt, R=N_resamples, data.col="EasyComplicated")

bootES(namibian, R=N_resamples, data.col="EasyComplicated")
bootES(german, R=N_resamples, data.col="EasyComplicated")

```

## User Experience - EfficientInefficient

```{r}

# no factor affected the ratings
EfficientInefficientModel <- lm (EfficientInefficient ~ DisplayType + Culture + QueryType 
                  + BasicComputerSkills + SpatialAnalysis + Webgis + WebmapUse + Programming 
                  + GeodataSearching + MapMaking + GeoportalFrequency, data = data)
summary(EfficientInefficientModel)

ggplot(data, aes(y = EfficientInefficient, x= DisplayType, fill=DisplayType)) +
  geom_boxplot() +  scale_fill_manual(values = c("#94d0f2", "#edd882"))
bootES(data, R=N_resamples, data.col="EfficientInefficient", group.col="DisplayType", contrast= c("LB", "LBM"))

ggplot(data, aes(y = EfficientInefficient, x= QueryType, fill=QueryType)) +
  geom_boxplot() +  scale_fill_manual(values = c("#94d0f2", "#edd882"))
bootES(data, R=N_resamples, data.col="EfficientInefficient", group.col="QueryType", contrast= c("ST", "STT"))

ggplot(data, aes(y = EfficientInefficient, x= Culture, fill=Culture)) +
  geom_boxplot() +  scale_fill_manual(values = c("#94d0f2", "#edd882"))
bootES(data, R=N_resamples, data.col="EfficientInefficient", group.col="Culture", contrast= c("namibian", "german"))

# Interaction effects
boxplot(EfficientInefficient ~ DisplayType * Culture, data = data)
boxplot(EfficientInefficient ~ QueryType * Culture, data = data)
boxplot(EfficientInefficient ~ QueryType * DisplayType, data = data)


efficientDC <- lm (EfficientInefficient ~ DisplayType * Culture, data = data)
efficientQC <- lm (EfficientInefficient ~ QueryType * Culture, data = data)
efficientQD <- lm (EfficientInefficient ~ QueryType * DisplayType, data = data)
summary(efficientDC)
summary(efficientQC)
summary(efficientQD)

# testing interaction more systematically
#easyQC_reduced <- lm (EfficientInefficient ~ QueryType + Culture, data = data)
#anova(easyQC, easyQC_reduced)

# interaction plot (simple)
#interaction.plot(x.factor = data$QueryType, 
#                 trace.factor = data$Culture,  
#                 response = data$EfficientInefficient, fun = mean)

# interaction plot in ggplot2
# https://sebastiansauer.github.io/vis_interaction_effects/
data %>% 
  group_by(QueryType, Culture) %>% 
  summarise(rating_groups = mean(EfficientInefficient)) -> ratings2

ratings2 %>% 
  ggplot() +
  aes(x = QueryType, y = rating_groups, color = Culture) +
  geom_line(aes(group = Culture)) +
  geom_point() + labs(y= "Mean of EfficientInefficient Ratings")

# Obtain the mean, with confidence interval values

bootES(data, R=N_resamples, data.col="EfficientInefficient")

bootES(lb, R=N_resamples, data.col="EfficientInefficient")
bootES(lbm, R=N_resamples, data.col="EfficientInefficient")

bootES(st, R=N_resamples, data.col="EfficientInefficient")
bootES(stt, R=N_resamples, data.col="EfficientInefficient")

bootES(namibian, R=N_resamples, data.col="EfficientInefficient")
bootES(german, R=N_resamples, data.col="EfficientInefficient")


```

## User Experience - ClearConfusing

```{r}
# MapMaking could have possibly affected the ratings
ClearConfusingModel <- lm (ClearConfusing ~ DisplayType + Culture + QueryType 
                  + BasicComputerSkills + SpatialAnalysis + Webgis + WebmapUse + Programming 
                  + GeodataSearching + MapMaking + GeoportalFrequency, data = data)
summary(ClearConfusingModel)

ggplot(data, aes(y = ClearConfusing, x= DisplayType, fill=DisplayType)) +
  geom_boxplot() +  scale_fill_manual(values = c("#94d0f2", "#edd882"))
bootES(data, R=N_resamples, data.col="ClearConfusing", group.col="DisplayType", contrast= c("LB", "LBM"))

ggplot(data, aes(y = ClearConfusing, x= QueryType, fill=QueryType)) +
  geom_boxplot() +  scale_fill_manual(values = c("#94d0f2", "#edd882"))
bootES(data, R=N_resamples, data.col="ClearConfusing", group.col="QueryType", contrast= c("ST", "STT"))

ggplot(data, aes(y = ClearConfusing, x= Culture, fill=Culture)) +
  geom_boxplot() +  scale_fill_manual(values = c("#94d0f2", "#edd882"))
bootES(data, R=N_resamples, data.col="ClearConfusing", group.col="Culture", contrast= c("namibian", "german"))

# Interaction effects
boxplot(ClearConfusing ~ DisplayType * Culture, data = data)
boxplot(ClearConfusing ~ QueryType * Culture, data = data)
boxplot(ClearConfusing ~ QueryType * DisplayType, data = data)


clearDC <- lm (ClearConfusing ~ DisplayType * Culture, data = data)
clearQC <- lm (ClearConfusing ~ QueryType * Culture, data = data)
clearQD <- lm (ClearConfusing ~ QueryType * DisplayType, data = data)
summary(clearDC)
summary(clearQC)
summary(clearQD)

# testing interaction more systematically
#easyQC_reduced <- lm (EfficientInefficient ~ QueryType + Culture, data = data)
#anova(easyQC, easyQC_reduced)

# interaction plot (simple)
#interaction.plot(x.factor = data$QueryType, 
#                 trace.factor = data$Culture,  
#                 response = data$EfficientInefficient, fun = mean)

# interaction plot in ggplot2
# https://sebastiansauer.github.io/vis_interaction_effects/
data %>% 
  group_by(QueryType, Culture) %>% 
  summarise(rating_groups = mean(ClearConfusing)) -> ratings2

ratings2 %>% 
  ggplot() +
  aes(x = QueryType, y = rating_groups, color = Culture) +
  geom_line(aes(group = Culture)) +
  geom_point() + labs(y= "Mean of ClearConfusing Ratings")

# Obtain the mean, with confidence interval values

bootES(data, R=N_resamples, data.col="ClearConfusing")

bootES(lb, R=N_resamples, data.col="ClearConfusing")
bootES(lbm, R=N_resamples, data.col="ClearConfusing")

bootES(st, R=N_resamples, data.col="ClearConfusing")
bootES(stt, R=N_resamples, data.col="ClearConfusing")

bootES(namibian, R=N_resamples, data.col="ClearConfusing")
bootES(german, R=N_resamples, data.col="ClearConfusing")
```

## User Experience - ExcitingBoring

```{r}
# ExcitingBoring could have possibly affected the ratings
ExcitingBoringModel <- lm (ExcitingBoring ~ DisplayType + Culture + QueryType 
                  + BasicComputerSkills + SpatialAnalysis + Webgis + WebmapUse + Programming 
                  + GeodataSearching + MapMaking + GeoportalFrequency, data = data)
summary(ExcitingBoringModel)

ggplot(data, aes(y = ExcitingBoring, x= DisplayType, fill=DisplayType)) +
  geom_boxplot() +  scale_fill_manual(values = c("#94d0f2", "#edd882"))
bootES(data, R=N_resamples, data.col="ExcitingBoring", group.col="DisplayType", contrast= c("LB", "LBM"))

ggplot(data, aes(y = ExcitingBoring, x= QueryType, fill=QueryType)) +
  geom_boxplot() +  scale_fill_manual(values = c("#94d0f2", "#edd882"))
bootES(data, R=N_resamples, data.col="ExcitingBoring", group.col="QueryType", contrast= c("ST", "STT"))

ggplot(data, aes(y = ExcitingBoring, x= Culture, fill=Culture)) +
  geom_boxplot() +  scale_fill_manual(values = c("#94d0f2", "#edd882"))
bootES(data, R=N_resamples, data.col="ExcitingBoring", group.col="Culture", contrast= c("namibian", "german"))

# Interaction effects
boxplot(ExcitingBoring ~ DisplayType * Culture, data = data)
boxplot(ExcitingBoring ~ QueryType * Culture, data = data)
boxplot(ExcitingBoring ~ QueryType * DisplayType, data = data)


boringDC <- lm (ExcitingBoring ~ DisplayType * Culture, data = data)
boringQC <- lm (ExcitingBoring ~ QueryType * Culture, data = data)
boringQD <- lm (ExcitingBoring ~ QueryType * DisplayType, data = data)
summary(boringDC)
summary(boringQC)
summary(boringQD)

# testing interaction more systematically
#easyQC_reduced <- lm (EfficientInefficient ~ QueryType + Culture, data = data)
#anova(easyQC, easyQC_reduced)

# interaction plot (simple)
#interaction.plot(x.factor = data$QueryType, 
#                 trace.factor = data$Culture,  
#                 response = data$EfficientInefficient, fun = mean)

# interaction plot in ggplot2
# https://sebastiansauer.github.io/vis_interaction_effects/
# data %>% 
#   group_by(QueryType, Culture) %>% 
#   summarise(rating_groups = mean(ExcitingBoring)) -> ratings2
# 
# ratings2 %>% 
#   ggplot() +
#   aes(x = QueryType, y = rating_groups, color = Culture) +
#   geom_line(aes(group = Culture)) +
#   geom_point() + labs(y= "Mean of ExcitingBoring Ratings")

# Obtain the mean, with confidence interval values

bootES(data, R=N_resamples, data.col="ExcitingBoring")


bootES(lb, R=N_resamples, data.col="ExcitingBoring")
bootES(lbm, R=N_resamples, data.col="ExcitingBoring")

bootES(st, R=N_resamples, data.col="ExcitingBoring")
bootES(stt, R=N_resamples, data.col="ExcitingBoring")

bootES(namibian, R=N_resamples, data.col="ExcitingBoring")
bootES(german, R=N_resamples, data.col="ExcitingBoring")

```

## User Experience - InterestingNotinteresting

```{r}

# No factor affected the ratings
InterestingNotinterestingModel <- lm (InterestingNotinteresting ~ DisplayType + Culture + QueryType 
                  + BasicComputerSkills + SpatialAnalysis + Webgis + WebmapUse + Programming 
                  + GeodataSearching + MapMaking + GeoportalFrequency, data = data)
summary(InterestingNotinterestingModel)


ggplot(data, aes(y = InterestingNotinteresting, x= DisplayType, fill=DisplayType)) +
  geom_boxplot() +  scale_fill_manual(values = c("#94d0f2", "#edd882"))
bootES(data, R=N_resamples, data.col="InterestingNotinteresting", group.col="DisplayType", contrast= c("LB", "LBM"))

ggplot(data, aes(y = InterestingNotinteresting, x= QueryType, fill=QueryType)) +
  geom_boxplot() +  scale_fill_manual(values = c("#94d0f2", "#edd882"))
bootES(data, R=N_resamples, data.col="InterestingNotinteresting", group.col="QueryType", contrast= c("ST", "STT"))

ggplot(data, aes(y = InterestingNotinteresting, x= Culture, fill=Culture)) +
  geom_boxplot() +  scale_fill_manual(values = c("#94d0f2", "#edd882"))
bootES(data, R=N_resamples, data.col="InterestingNotinteresting", group.col="Culture", contrast= c("namibian", "german"))

# Interaction effects
boxplot(InterestingNotinteresting ~ DisplayType * Culture, data = data)
boxplot(InterestingNotinteresting ~ QueryType * Culture, data = data)
boxplot(InterestingNotinteresting ~ QueryType * DisplayType, data = data)


interestingDC <- lm (InterestingNotinteresting ~ DisplayType * Culture, data = data)
interestingQC <- lm (InterestingNotinteresting ~ QueryType * Culture, data = data)
interestingQD <- lm (InterestingNotinteresting ~ QueryType * DisplayType, data = data)
summary(interestingDC)
summary(interestingQC)
summary(interestingQD)

# testing interaction more systematically
interestingDC_reduced <- lm (InterestingNotinteresting ~ QueryType + Culture, data = data)
anova(interestingDC, interestingDC_reduced)

#interaction plot (simple)
interaction.plot(x.factor = data$DisplayType,
                trace.factor = data$Culture,
                response = data$InterestingNotinteresting, fun = mean)

# interaction plot in ggplot2
# https://sebastiansauer.github.io/vis_interaction_effects/
#data %>% 
#   group_by(DisplayType, Culture) %>% 
#   summarise(rating_groups = mean(InterestingNotinteresting)) -> ratings2
# 
# ratings2 %>% 
#   ggplot() +
#   aes(x = DisplayType, y = rating_groups, color = Culture) +
#   geom_line(aes(group = Culture)) +
#   geom_point() + labs(y= "Mean of InterestingNotinteresting Ratings")

# Obtain the mean, with confidence interval values

bootES(data, R=N_resamples, data.col="InterestingNotinteresting")

bootES(lb, R=N_resamples, data.col="InterestingNotinteresting")
bootES(lbm, R=N_resamples, data.col="InterestingNotinteresting")

bootES(st, R=N_resamples, data.col="InterestingNotinteresting")
bootES(stt, R=N_resamples, data.col="InterestingNotinteresting")

bootES(namibian, R=N_resamples, data.col="InterestingNotinteresting")
bootES(german, R=N_resamples, data.col="InterestingNotinteresting")


```

## User Experience - InventiveConventional

```{r}

# No factor affected the ratings
InventiveConventionalModel <- lm (InventiveConventional ~ DisplayType + Culture + QueryType + BasicComputerSkills + SpatialAnalysis + Webgis + WebmapUse + Programming           + GeodataSearching + MapMaking + GeoportalFrequency, data = data)
summary(InventiveConventionalModel)


ggplot(data, aes(y = InventiveConventional, x= DisplayType, fill=DisplayType)) +
  geom_boxplot() +  scale_fill_manual(values = c("#94d0f2", "#edd882"))
bootES(data, R=N_resamples, data.col="InventiveConventional", group.col="DisplayType", contrast= c("LB", "LBM"))

ggplot(data, aes(y = InventiveConventional, x= QueryType, fill=QueryType)) +
  geom_boxplot() +  scale_fill_manual(values = c("#94d0f2", "#edd882"))
bootES(data, R=N_resamples, data.col="InventiveConventional", group.col="QueryType", contrast= c("ST", "STT"))

ggplot(data, aes(y = InventiveConventional, x= Culture, fill=Culture)) +
  geom_boxplot() +  scale_fill_manual(values = c("#94d0f2", "#edd882"))
bootES(data, R=N_resamples, data.col="InventiveConventional", group.col="Culture", contrast= c("namibian", "german"))

# Interaction effects
boxplot(InventiveConventional ~ DisplayType * Culture, data = data)
boxplot(InventiveConventional ~ QueryType * Culture, data = data)
boxplot(InventiveConventional ~ QueryType * DisplayType, data = data)


inventiveDC <- lm (InventiveConventional ~ DisplayType * Culture, data = data)
inventiveQC <- lm (InventiveConventional ~ QueryType * Culture, data = data)
inventiveQD <- lm (InventiveConventional ~ QueryType * DisplayType, data = data)
summary(inventiveDC)
summary(inventiveQC)
summary(inventiveQD)

# testing interaction more systematically
#interestingDC_reduced <- lm (InterestingNotinteresting ~ QueryType + Culture, data = data)
#anova(interestingDC, interestingDC_reduced)

#interaction plot (simple)
interaction.plot(x.factor = data$DisplayType,
                trace.factor = data$Culture,
                response = data$InventiveConventional, fun = mean)

# interaction plot in ggplot2
# https://sebastiansauer.github.io/vis_interaction_effects/
#data %>% 
#   group_by(DisplayType, Culture) %>% 
#   summarise(rating_groups = mean(InterestingNotinteresting)) -> ratings2
# 
# ratings2 %>% 
#   ggplot() +
#   aes(x = DisplayType, y = rating_groups, color = Culture) +
#   geom_line(aes(group = Culture)) +
#   geom_point() + labs(y= "Mean of InterestingNotinteresting Ratings")

# Obtain the mean, with confidence interval values

bootES(data, R=N_resamples, data.col="InventiveConventional")

bootES(lb, R=N_resamples, data.col="InventiveConventional")
bootES(lbm, R=N_resamples, data.col="InventiveConventional")

bootES(st, R=N_resamples, data.col="InventiveConventional")
bootES(stt, R=N_resamples, data.col="InventiveConventional")

bootES(namibian, R=N_resamples, data.col="InventiveConventional")
bootES(german, R=N_resamples, data.col="InventiveConventional")


```

## User Experience - LeadingEdgeStandard

```{r}
# Culture (and Geodatasearching, QueryType) affected the ratings
LeadingedgeStandardModel <- lm (LeadingedgeStandard ~ DisplayType + Culture + QueryType 
                  + BasicComputerSkills + SpatialAnalysis + Webgis + WebmapUse + Programming 
                  + GeodataSearching + MapMaking + GeoportalFrequency, data = data)
summary(LeadingedgeStandardModel)

ggplot(data, aes(y = LeadingedgeStandard, x= DisplayType, fill=DisplayType)) +
  geom_boxplot() +  scale_fill_manual(values = c("#94d0f2", "#edd882"))
bootES(data, R=N_resamples, data.col="LeadingedgeStandard", group.col="DisplayType", contrast= c("LB", "LBM"))

ggplot(data, aes(y = LeadingedgeStandard, x= QueryType, fill=QueryType)) +
  geom_boxplot() +  scale_fill_manual(values = c("#94d0f2", "#edd882"))
bootES(data, R=N_resamples, data.col="LeadingedgeStandard", group.col="QueryType", contrast= c("ST", "STT"))

ggplot(data, aes(y = LeadingedgeStandard, x= Culture, fill=Culture)) +
  geom_boxplot() +  scale_fill_manual(values = c("#94d0f2", "#edd882"))
bootES(data, R=N_resamples, data.col="LeadingedgeStandard", group.col="Culture", contrast= c("namibian", "german"))

# Interaction effects
boxplot(LeadingedgeStandard ~ DisplayType * Culture, data = data)
boxplot(LeadingedgeStandard ~ QueryType * Culture, data = data)
boxplot(LeadingedgeStandard ~ QueryType * DisplayType, data = data)


leadingedgeDC <- lm (LeadingedgeStandard ~ DisplayType * Culture, data = data)
leadingedgeQC <- lm (LeadingedgeStandard ~ QueryType * Culture, data = data)
leadingedgeQD <- lm (LeadingedgeStandard ~ QueryType * DisplayType, data = data)
summary(leadingedgeDC)
summary(leadingedgeQC)
summary(leadingedgeQD)

# testing interaction more systematically (Q)
leadingedgeQD_reduced <- lm (LeadingedgeStandard ~ QueryType + DisplayType, data = data)
anova(leadingedgeQD, leadingedgeQD_reduced)

#interaction plot (simple)
interaction.plot(x.factor = data$DisplayType,
                trace.factor = data$QueryType,
                response = data$LeadingedgeStandard, fun = mean)

# interaction plot in ggplot2
# https://sebastiansauer.github.io/vis_interaction_effects/
data %>%
  group_by(DisplayType, QueryType) %>%
  summarise(rating_groups = mean(InterestingNotinteresting)) -> ratings2

ratings2 %>%
  ggplot() +
  aes(x = DisplayType, y = rating_groups, color = QueryType) +
  geom_line(aes(group = QueryType)) +
  geom_point() + labs(y= "Mean of LeadingedgeStandard Ratings")

# Obtain the mean, with confidence interval values

bootES(data, R=N_resamples, data.col="LeadingedgeStandard")


bootES(lb, R=N_resamples, data.col="LeadingedgeStandard")
bootES(lbm, R=N_resamples, data.col="LeadingedgeStandard")

bootES(st, R=N_resamples, data.col="LeadingedgeStandard")
bootES(stt, R=N_resamples, data.col="LeadingedgeStandard")

bootES(namibian, R=N_resamples, data.col="LeadingedgeStandard")
bootES(german, R=N_resamples, data.col="LeadingedgeStandard")

```

## Tests of significance for background Variables

```{r}

library(Hmisc)

# ComplexityRatings ~  MapMaking => no
ComplexityVSmapmaking <- lm(formula = ComplexityRatings ~  MapMaking, data = data)
summary(ComplexityVSmapmaking)

# EasyComplicated ~ GeodataSearching => no 
EasyVSsearching <- lm(formula = EasyComplicated ~ GeodataSearching, data = data)
summary(EasyVSsearching)

# ClearConfusing ~ MapMaking => no
ClearVSmapmaking <- lm (ClearConfusing ~ MapMaking, data = data)
summary(ClearVSmapmaking)

# ExcitingBoring ~ GeodataSearching => no
ExcitingVSsearching <- lm (ExcitingBoring ~ GeodataSearching, data = data)
summary(ExcitingVSsearching)

# LeadingedgeStandard ~ GeodataSearching => no
LeadingVSsearching <- lm (LeadingedgeStandard ~ GeodataSearching, data = data)
summary(LeadingVSsearching)

# LeadingedgeStandard ~ QueryType => no
LeadingVSquery <- lm (LeadingedgeStandard ~ QueryType, data = data)
summary(LeadingVSquery)

# DCG3 ~ SpatialAnalysis => no
dcg3VSspatialanalysis <- lm(formula = DCG3 ~ SpatialAnalysis, data = data)
summary(dcg3VSspatialanalysis)

# DCG5 vs WebmapUse => no
dcg5VSwebmapuse <- lm(formula = DCG5 ~ WebmapUse, data = data)
summary(dcg5VSwebmapuse)

# DCG5 ~ GeodataSearching => no
dcg5VSsearching <- lm(formula = DCG5 ~ GeodataSearching, data = data)
summary(dcg5VSsearching)

# ComplexityRatings ~  WebmapUse => yes
complexityVSwebmapuse <- lm(formula = ComplexityRatings ~  WebmapUse, data = data)
summary(complexityVSwebmapuse)

```

## ComplexityRatings VS Webmapuse Skills

```{r}

library(Hmisc)

data$WMU <- as.factor(data$WebmapUse)
boxplot(ComplexityRatings ~ WMU, data=data)

summary(lm(formula = ComplexityRatings ~  WMU, data = data))

ggplot(data, aes(y = ComplexityRatings, x= WMU, fill=WMU)) +
  geom_boxplot() + labs(x= "Web map use skills (WMU)")

example <- subset(data, select = c("ComplexityRatings", "WebmapUse"))
corr_matrix <- rcorr(as.matrix(example), type = "pearson")
print(corr_matrix)

```


